---
title: "HackerRank Email Opening Prediction"
author: "Vinh Dang"
date: "September 4, 2016"
output: pdf_document
---


#Data Preprocessing

The problem is defined as, given an email with several pre-calculated features, we need to predict whether or not this email will be opened by users.

The first task is obviously reading datasets

```{r}
train = read.csv("training_dataset.csv")
test = read.csv("test_dataset.csv")
```

Let's take a look into two datasets

```{r}
str(train)
```

```{r}
str(test)
```

Several features appeared uniquely in train dataset. While I am not intending to use any unsupervised techniques, they should be removed.

```{r}
train$click_time = NULL
train$clicked = NULL
train$open_time = NULL
train$unsubscribe_time = NULL
train$unsubscribed = NULL
```

What is the distribution of the train set

```{r}
summary (train$opened)

```

Seems that the opened emails cover 66% of the train dataset (majority threshold). Any predictive model should do better than that.

# Model Selection

The problem is a binary-classification. I validated three predictive models: logistic regression, random forest and deep feed-forward neural network (DNN).

Using 5-folds cross validation on the training dataset, we chose DNN as our final model, because it achieved the best F1-score and accuracy in compare to other models.